HI and OVI Emission from the Circum-Galactic Medium with a large sample of cosmological hydrodynamical simulations

### 2016-03-28 ms_oviemission.tex
uncomplete draft in 28 Mar

\documentclass[useAMS,usenatbib]{mn2e}
\input psfig.sty
\usepackage{array}
%\usepackage{graphicx}
%\usepackage{epstopdf}

@@

\title[OVI Emssivity] {}

\author[Zhang et al.]{Shuinai Zhang$^{1}$\thanks{snzhang@pmo.ac.cn}, Liang Wang$^{1,3}$,Taotao Fang$^{2}$, Li Ji$^{1}$,
\newauthor{Thales Gutcke$^3$, Andrea V. Macci\`o$^{3,4}$}, Xi Kang$^{1}$\\
$^1$Purple Mountain Observatory, 2 West Beijing Road, Nanjing 210008, China\\
$^2$Xiamen Univeristy \\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
$^4$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE}
\begin{document}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to study ultra-violet (UV)
  emission from circum-galactic medium (CGM) in galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses. We analyze the spatially-extended structures of emission lines
  from OVI and Ly$alpha$.
\end{abstract}

@@

This paper is organized as follows: The cosmological hydrodynamical
simulations and the methodology for computing metal line emission
are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
we present the results including the Ly$alpha$ and OVI emission map,
surface brightness and luminosity evolutions of all galaxies in NIHAO
sample; \S\ref{sec:sum} gives discussion and  summary of our
results.

@@

We first assign the number densities and temperatures of all gas particles
inside $2 R_{\rm vir}$ to $200\times 200 \times 200$ grids according SPH
spline kernel \citep{Monaghan85}:
\begin{equation}
W\left(r,h\right) = \frac{8}{\pi h^3}
  %\begin{cases}
  %1-6\left(\frac{r}{h}\right)^2+6\left(\frac{r}{h}\right)^3, & \quad 0\leq\frac{r}{h}\leq\frac{1}{2},\\
  %2\left(1-\frac{r}{h}\right)^3, & \quad \frac{1}{2} < \frac{r}{h} \leq 1,\\
  %0, & \quad \frac{r}{h} >1.\\
  %\end{cases}
\end{equation}

The emissivities are computed as a function of gas temperature and

@@

@@

@@

%Evolution of the Mass-Metallicity Relations in Passive and Star-forming Galaxies from SPH-cosmological Simulations

%Multiphase smoothed-particle hydrodynamics
%\bibitem[Ritchie \& Thomas(2001)]{Ritchie01} Ritchie, B.~W.,
%  \& Thomas, P.~A.\ 2001, \mnras, 323, 743

@@

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\input psfig.sty
\usepackage{array}
%\usepackage{graphicx}
%\usepackage{epstopdf}
\usepackage{amsmath}

@@

\title[OVI Emssivity] {HI and OVI Emission from the Circum-Galactic Medium
 with a large sample of cosmological hydrodynamical simulations}

\author[Zhang et al.]{Shuinai Zhang$^{1}$\thanks{snzhang@pmo.ac.cn}, Liang Wang$^{1,3}$,Taotao Fang$^{2}$, Li Ji$^{1}$,Thales Gutcke$^3$, 
\newauthor{Andrea V. Macci\`o$^{3,4}$, Xi Kang$^{1}$}\\
$^1$Purple Mountain Observatory, 2 West Beijing Road, Nanjing 210008, China\\
$^2$Xiamen Univeristy, Xiamen, China \\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
$^4$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE}
\begin{document}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to study ultra-violet (UV)
  emission from circum-galactic medium (CGM) in galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses. We analyze the spatially-extended structures of emission lines
  from OVI and Ly$\alpha$.
\end{abstract}

@@

{\bf Why the CGM is important}

The hot and cold gas phases were indicated by OVI and HI ions in observation
commomly.

{\bf What can we gain from  HI and OVI in CGM}

\citet{Gutcke16} compared the column density profiles of OVI and HI
in CGM with observations.

{\bf What is the advantage of emssion line of HI and OVI}

\citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
of high-redshift ($z=2-4$) galaxies using cosmological simulations from the 
Feedback in Realistic Environments (FIRE) project.

This paper is organized as follows: The cosmological hydrodynamical
simulations and the methodology for computing metal line emission
are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
we present the results including the Ly$\alpha$ and OVI emission map,
surface brightness and luminosity evolutions of all galaxies in NIHAO
sample; \S\ref{sec:sum} gives discussion and  summary of our
results.

@@

We first assign the hydrogen number densities and temperatures of all gas 
particles inside $2 \Rvir$ to $200\times 200 \times 200$ grids 
according SPH spline kernel \citep{Monaghan85}:
\begin{equation}
W\left(r,h\right) = \frac{8}{\pi h^3}
  \begin{cases}
  1-6\left(\frac{r}{h}\right)^2+6\left(\frac{r}{h}\right)^3,  &\quad 0\leq\frac{r}{h}\leq\frac{1}{2},\\
  2\left(1-\frac{r}{h}\right)^3,  &\quad \frac{1}{2} < \frac{r}{h} \leq 1,\\
  0,  &\quad \frac{r}{h} >1.\\
  \end{cases}
\end{equation}
The distribution of emissivities are then computed as a function of 
gas temperature and hydroden number density on each grid by bi-linearly 
interplating the grids of emissivities generated using CLOUDY 
({\bf version and citation}).
The temperature of the grids are in the range $?? < T < ??$K in intervals of
$\Delta \log_{10} T = ?.??$ and hydrogen number densities are in the range
$?? < n_H < ?? {\rm cm}^{-3}$ in intervals of $\Delta \log_{10} n_H = ??$.
The grids are computed at redshift z = 0 assuming gas is of solar metallicity,
optical thin and {\bf blabla}.

To compute the HI neutral fraction, like \citep{Gutcke16}, we used the 
self-shielding approximation presented in \citep{Rahmati13}.
{\bf say more detail about it}. Contrastly, To compute the OVI, the 
self-shielding approximation is not necessary to consider. {\bf reason}

\subsection{Luminosity Calculation}
\label{sec:lum}

In order to estimate the evolution of total OVI and HI luminosities inside
$2 \Rvir$, we employ the grids 
of emissivities computed since z=4 to present to evaluate the evolution of 
luminosities of all galaxies in NIHAO sample from particle data directly.
The method is similar to the one used by \citep{Sravan15}, the OVI and HI 
luminosities of each gas particle are calculated as
\begin{equation}
L = \epsilon_{\odot}\left(z,n_H,T\right)\left(\frac{m_{gas}}{\rho_{gas}}\right)
    \left(\frac{Z_{gas}}{Z_{\odot}}\right),
\end{equation}
where $m_{gas}$, $\rho_{gas}$ and $Z_{gas}$ are the mass, density and 
metallicity of the gas particle, and $\epsilon_{\odot}\left(z,n_H,T\right)$
is the emissivity interpolated bi-linearly from pre-computed grids of 
emissivities with given redshift, hydrogen number density and temperature.

@@

\subsection{OVI and HI Emissivity Maps and Radial Profile}
\label{sec:map_rp}

\subsection{Evolution of Luminosities}
\label{sec:evo}

@@

\bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956

@@

%Impact of local stellar radiation on the H I column density distribution
\bibitem[Rahmati et al.(2013)]{Rahmati13} Rahmati, A., Schaye, J., Pawlik, A.~H., Rai{\v c}evi{\'c}, M., 2013, MNRAS, 431,2261

@@

%Strongly Time-Variable Ultra-Violet Metal Line Emission from the Circum-Galactic Medium of High-Redshift Galaxies
\bibitem[Sravan et al.(2015)]{Sravan15} Sravan, N., Faucher-Gigu{\`e}re, C.~-A., van de Voort, F., et al.\ 2015, arXiv:1510.06410
